\documentclass[12pt]{article}

\usepackage{amssymb, amsmath, amsfonts}
\usepackage{moreverb}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[margin=0.75in]{geometry}
\usepackage{graphics}
\usepackage{color}
\usepackage{array}
\usepackage{float}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage[makeroom]{cancel}
\usepackage{bbold}
\usepackage{alltt}
\usepackage{physics}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows}
\usepackage{pgfplots}
\usepackage{bigints}
\allowdisplaybreaks
\pgfplotsset{compat=1.12}

\theoremstyle{plain}
\newtheorem*{theorem*}{Theorem}
\newtheorem{theorem}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem{lemma}{Lemma}

\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newcommand{\E}{\varepsilon}
\def\Rl{\mathbb{R}}
\def\Cx{\mathbb{C}}

\title{\bf HW \#3}
\author{\bf Sam Fleischer}
\date{\bf February 05, 2015}

\pgfplotsset{compat=1.12}

\begin{document}
\textbf{MATH 207B \hfill Applied Math \ \ \hfill Winter 2016\ \ \ }

{\let\newpage\relax\maketitle}

\section*{Problem 1}
\emph{Suppose that $u(x)$ is a non-zero solution of the eigenvalue problem}
\begin{align*}
    \begin{array}{rr}
        -u'' = \lambda u, &\qquad 0 < x < 1,\\
        u(0) = 0, & u(1) = 0.
    \end{array}
\end{align*}
\emph{Show that}
\begin{align*}
    \lambda = \frac{\int_0^1 (u')^2 \dd x}{\int_0^1 u^2 \dd x}.
\end{align*}
\emph{Deduce that every eigenvalue $\lambda$ is strictly positive.}

\section*{Problem 2}
\emph{Heat flows in a rod of length $L$ with a heat source $(a > 0)$ or sink $(a < 0)$ whose density $au$ is proportional to the temperature $u$.  Suppose that $u(x,t)$ satisfies the IBVP}
\begin{align*}
    \begin{array}{rrr}
        u_t = Du_{xx} + au, & \qquad 0 < x < L, & \qquad t > 0, \\
        u(0, t) = 0, & u(L, t) = 0, & \\
        u(x, 0) = f(x). & &
    \end{array}
\end{align*}
\begin{enumerate}[\bf (a)]
    \item
        \emph{Nondimensionalize the problem, and show that the IBVP can be written in nondimensional form as}
        \begin{align*}
            \begin{array}{rrr}
                u_t = u_{xx} + \alpha u, & \qquad 0 < x < 1, & \qquad t > 0, \\
                u(0, t) = 0, & u(1, t) = 0, & t > 0, \\
                u(x, 0) = f(x). & &
            \end{array}
        \end{align*}
        \emph{where $\alpha$ is a suitable nondimensional parameter.  Give a physical interpretation of $\alpha$.}
    \item
        \emph{Solve the IBVP in \textbf{(a)} be the method of separation of variables.}
    \item
        \emph{How does your solution behave as $t \rightarrow \infty$?  For what values of $\alpha$ does $u(x,t) \rightarrow 0$ as $t \rightarrow \infty$?  What happens for larger values of $\alpha$?  Give a physical explanation of this behavior in terms of the thermal energy.}
\end{enumerate}

\section*{Problem 3}
\emph{Solve the following eigenvalue problem for the linear operator $-\frac{\dd^2}{\dd x^2}$ with Neumann BCs:}
\begin{align*}
    \begin{array}{rr}
        -u'' = \lambda u, & \qquad 0 < x < 1, \\
        u'(0) = 0, & u'(1) = 0.
    \end{array}
\end{align*}
\begin{enumerate}[\bf (a)]
    \item 
        \emph{Find the eigenvalues $\lambda = \lambda_n$, where $n = 0, 1, 2, \dots$, and the corresponding eigenfunctions $u_n(x)$.}
    \item
        \emph{Show that the eigenfunctions can be normalized so that}
        \begin{align*}
            \int_0^1 u_m(x) u_n(x) \dd x = \delta_{mn} = \begin{cases}
                1 & \text{ if }m = n \\
                0 & \text{ if }m \neq n
            \end{cases}
        \end{align*}
        \emph{where $\delta$ is the Kronecker Delta.}
    \item
        \emph{Does your argument in \textbf{Problem 1} that $\lambda \neq 0$ work in this case?}
\end{enumerate}

\section*{Problem 4}
\begin{enumerate}[\bf (a)]
    \item
        \emph{Solve the following IBVP by the method of separation of variables}
        \begin{align*}
            \begin{array}{rrr}
                u_t = u_{xx}, & \qquad 0 < x < 1, & \qquad t > 0, \\
                u_x(0, t) = 0, & u_x(1, t) = 0 & t > 0 \\
                u(x, 0) = f(x) & 0 < x < 1
            \end{array}
        \end{align*}
    \item
        \emph{How does your solution behave as $t \rightarrow \infty$?}
    \item
        \emph{Show directly from the IBVP in \textbf{(a)} that}
        \begin{align*}
            \int_0^1 u(x, t) \dd x = \int_0^1 f(x) \dd x\ \ \ \ \text{ for all }t \geq 0.
        \end{align*}
        \emph{Is this result consistent with your answer in \textbf{(b)}?  Give a physical explanation of the long-term behavior of $u(x,t)$.}
\end{enumerate}

\end{document}
